Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Removed long edges manually for PBMC3k data
Changed colors og Figure 17

@@

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist)

@@

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c('#ff7f00', '#4daf4a')) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c('#ff7f00', '#4daf4a')) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1, 0.6)) +
  ylim(c(-1, 0.6)) +
  interior_annotation("b") +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c('#ff7f00', '#4daf4a')) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("c") +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model3 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c('#ff7f00', '#4daf4a')) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.6)) +
  ylim(c(-1, 0.6)) +
  interior_annotation("d") +
  theme(
    legend.position = "none"
  )

>>>>

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc) |>
  filter(!(row_number() %in% c(6, 12, 14, 16, 17, 19, 23, 29, 30, 143, 144, 146, 147, 157)))

@@

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) |>
  filter(!(row_number() %in% c(143, 144, 162)))

@@

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1, 0.6)) +
  ylim(c(-1, 0.6)) +
  interior_annotation("b") +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("c") +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model3 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.2,
    alpha = 0.3) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.6)) +
  ylim(c(-1, 0.6)) +
  interior_annotation("d") +
  theme(
    legend.position = "none"
  )
